---
title: "WFUrbanAdaptation"
output:
  md_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# WFUrbanAdaptation

WFUrbanAdaptation is a research compendium that brings together the data and analyses associated with Homola et al. (in review). R scripts are provided in analysis/, human-readable data in extData/, and R-readable data in an .rda file in data/. 

Note: All analyses originally conducted and package built using R version 3.5.1 in Windows 10

### To get started using the package

```{r eval=FALSE}
options(repos=structure(c(CRAN="http://cran.r-project.org")))
install.packages("devtools")
library(devtools)
install_github("jaredhomola/WFUrbanAdaptation")
```

### Scripts in /analysis
1. buildRDA.R: Build RDA file
2. installPackages.R: Install required packages
3. envPCA.R: PCA of environmental variables
4. genDiversity.R: Genetic diversity measures
5. diversityECDF.R: Genetic diversity empirical cumulative density function
6. neiGst.R: Genetic differentiation
7. multivariateAnalyses.R: Multivariate analyses including DAPCs and PCoAs
8. outlierAnalysis.R: Outlier analysis using percentile-based approach across replicates. Also include allele and genotype frequency plots.
9. logisticRegressionGEA.R: Genotype-environment association analysis using logistic regression

### Contact
Jared J. Homola  
jaredhomola20@gmail.com  
www.jaredhomola.com  


#### Copyright (c) 2018 Jared J. Homola

Permission is hereby granted, free of charge, to any person obtaining a copy of this software and associated documentation files (the "Software"), to deal in the Software without restriction, including without limitation the rights to use, copy, modify, merge, publish, distribute, sublicense, and/or sell copies of the Software, and to permit persons to whom the Software is furnished to do so, subject to the following conditions:

The above copyright notice and this permission notice shall be included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.
